Confirmation of Wide-Field Signatures in Redshifted 21~cm Power Spectra using Murchison Widefield Array Observations

### 2015-04-01 ms.tex
Add more emphasis in the Introduction
From 79304d5:
============

In ms.tex,

(*) Add emphasis on critical input for HERA and SKA in the Introduction

A recent study by \citet{thy15} using instrument and all-sky foreground models has shed new light on the significant role played by the interplay between foreground emission and the nature of wide-field measurements, typical of most modern EoR experiments and was noted to cause significant contamination in Fourier modes considered to be most sensitive for the cosmological H~{\sc i} signal. This paper presents a follow-up analysis of that study. By using a larger volume of MWA data obtained independently over different nights pointed at the same region of sky, we confirm with high significance the presence of certain key characteristics (referred to as the {\it pitchfork} signature) of wide-field measurements predicted in the preceding study.

>>>>

A recent study by \citet{thy15} using instrument and all-sky foreground models has shed new light on the significant role played by the interplay between foreground emission and the nature of wide-field measurements, typical of most modern EoR experiments. It was noted to cause significant contamination in Fourier modes considered to be most sensitive for the cosmological H~{\sc i} signal. It has been shown that a careful design of antenna aperture can significantly mitigate this contamination. And an optimal weighting of foreground-contaminated Fourier modes may be required to extract the signal with maximum sensitivity. Thus, knowledge of such detailed foreground signatures becomes essential for design and analysis choices of future instruments such as HERA and SKA. This paper presents a follow-up analysis of that study. By using a larger volume of MWA data obtained independently over different nights pointed at the same region of sky, we confirm with high significance the presence of certain key characteristics (referred to as the {\it pitchfork} signature) of wide-field measurements predicted in the preceding study.
